Reading Notes

### 2020-08-10 2pd.tex
Small compilation edits for eric; Added NSF review rubric for BI/IM.

<compare VOTCA's backmapping to my proposed scheme>
VOTCA makes some progress towards a TRUE simulation pipeline: they include a docker container with their pre-built software stack and example input files <see https://github.com/votca/votca -- using this code via docker> (but some of these input files don't work and the codecoverage on their repo as of time of writing is 0\%), and while including example inputs is a good first step, very little walkthrough (aside from code comments buried in the xml) is given.
A manual is provided but there is some disconnect between the example files and those given in the manual <https://github.com/votca/csg-manual/releases>.
the code is a mix of C++, shell commands, python, and interacts with compiled programs through the command-line and mpi.
which makes their working a little tenuous.
And judging by the amount of confusion in their mailing list <https://groups.google.com/forum/#!forum/votca> there is room for improvement in the API.
Overall though this is program has many features, interfaces with many popular MD engines (lammps, gromacs, hoomd), and is under active, collaborative development.
A good question might be if I'm so into OSS and collaboration--why don't I just contribute an MSIBI package to VOTCA.
This is a reasonable question.
The answer is because I find VOTCA to be near-overwhelming in it's scope and the cognitive load of trying to fit this whole project into my brain is not ideal.
I also don't like their API.
by choosing a pure python API I will be able to make use of jupyter notebooks which can be run on cloud servers using tools like mybinder <link mybinder, link to tutorials I;ve made> which can combine executable code with markdown text and images.
In this way a tutorial can provide exact commands needed to reproduce the example intimately connected with the rationale and justification of that example.
I would like to think that my code speaks for itself, but after reading other people's code, I have a renewed appreciation for explanations in paragraph form, diagrams, and figures.

>>>>

<compare VOTCA's backmapping to my proposed scheme>
VOTCA makes some progress towards a TRUE simulation pipeline: they include a docker container with their pre-built software stack and example input files <see https://github.com/votca/votca -- using this code via docker> (but some of these input files don't work and the codecoverage on their repo as of time of writing is 0\%), and while including example inputs is a good first step, very little walkthrough (aside from code comments buried in the xml) is given.
A manual is provided but there is some disconnect between the example files and those given in the manual <https://github.com/votca/csg-manual/releases>.
the code is a mix of C++, shell commands, python, and interacts with compiled programs through the command-line and mpi.
which makes their working a little tenuous.
And judging by the amount of confusion in their mailing list <https://groups.google.com/forum/\#!forum/votca> there is room for improvement in the API.
Overall though this is program has many features, interfaces with many popular MD engines (lammps, gromacs, hoomd), and is under active, collaborative development.
A good question might be if I'm so into OSS and collaboration--why don't I just contribute an MSIBI package to VOTCA.
This is a reasonable question.
The answer is because I find VOTCA to be near-overwhelming in it's scope and the cognitive load of trying to fit this whole project into my brain is not ideal.
I also don't like their API.
by choosing a pure python API I will be able to make use of jupyter notebooks which can be run on cloud servers using tools like mybinder <link mybinder, link to tutorials I;ve made> which can combine executable code with markdown text and images.
In this way a tutorial can provide exact commands needed to reproduce the example intimately connected with the rationale and justification of that example.
I would like to think that my code speaks for itself, but after reading other people's code, I have a renewed appreciation for explanations in paragraph form, diagrams, and figures.
